A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-03-27 index.Rmd
Reknit index with link to preprint
Add WAAA to acknowledgments for funding

## Links to manuscript
The manuscript publishing the results presented in this compendium can be found at ....

Preprint at .........

## Acknowledgments  
This meta-analysis was carried out with the funding assistance of the Grains Research and Development Corporation in Australia. Raw data for this work were contributed by the University of Southern Queensland, Queensland Department of Agriculture, Fisheries and Forestry (DAF), and the Northern Grower Alliance. Additional thanks to Malcolm Riley, Sue Thompson and Lawrie Price.

>>>>

## Links to manuscript

The preprint is available from agriRxiv: <https://doi.org/10.31220/agriRxiv.2021.00042>.

## Acknowledgments  
This meta-analysis was carried out with the funding assistance of the Grains Research and Development Corporation in Australia and the Western Australia Agriculture Authority. Raw data for this work were contributed by the University of Southern Queensland, Queensland Department of Agriculture, Fisheries and Forestry (DAF), and the Northern Grower Alliance. Additional thanks to Malcolm Riley, Sue Thompson and Lawrie Price.
